Body size patterns

### 2020-11-04 MS_Analysis_3spp_4rivers_Patterns_from 2spp_bySpp.Rmd
added flow/temp means

>>>>

```{r}
vB %>%
  group_by(season, riverOrdered) %>%
  summarize(meanT = mean(meanTemperature, na.rm = TRUE)) %>%
  ggplot(aes(season, meanT, color = riverOrdered)) +
  geom_point()

vB %>%
  group_by(season) %>%
  summarize(meanT = mean(meanTemperature, na.rm = TRUE))

vB %>%
  group_by(season, riverOrdered) %>%
  summarize(meanF = mean(meanFlow, na.rm = TRUE)) %>%
  ggplot(aes(season, meanF, color = riverOrdered)) +
  geom_point()

vB %>%
  group_by(season) %>%
  summarize(meanF = mean(meanFlow, na.rm = TRUE))
```
